Regular singular Volterra equations on complex domains

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Propose rewrite of sentence about Écalle

Our results build on known methods for solving differential equations with irregular singularities. Our focus on integral equations in the position domain, and the singularities of their solutions, recalls \textcolor{orange}{recalls the approach of \'Ecalle's theory of resurgence. However our method differs from the one of Loday-Richaud and Remy who instead used a formal approach to find solutions in the position domain~\cite{loday-Remy2011}.} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}. One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions. The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}. This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
\subsection{Formalism for coordinates}
\subsubsection{Rationale}
Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain. Each associated solution $\psi_\alpha$ is most easily expressed in terms of its own translated position coordinate $\zeta_\alpha = \zeta - \alpha$. We therefore expect our results to be used in calculations involving multiple coordinates. Our formalism for points, functions, and coordinates is tailored to such calculations.

>>>>

Our results build on known methods for solving differential equations with irregular singularities. Our focus on integral equations in the position domain, and the singularities of their solutions, \textcolor{cyan}{recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}. One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions.} \textcolor{pink}{recalls \textcolor{orange}{recalls the approach of \'Ecalle's theory of resurgence. However our method differs from the one of Loday-Richaud and Remy who instead used a formal approach to find solutions in the position domain~\cite{loday-Remy2011}.} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}. One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.} The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}. This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
\subsection{Formalism for coordinates}
\subsubsection{Rationale}
Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain. Each associated solution $\psi_\alpha$ is most easily expressed in terms of its own translated position coordinate $\zeta_\alpha = \zeta - \alpha$. We therefore expect our results to be used in calculations involving multiple coordinates. Our formalism for points, functions, and coordinates is tailored to such calculations.
